A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-09-15 paper/main.tex
clean validation analysis and its discussion

\subsection*{Data Legend}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a text-based Praat TextGrid file and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text}, \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

\begin{table*}[t]
\caption{Simple part-of-speech tagging (\texttt{pos}) performed by the Python package spaCy \citep{spacy2}.
All 15 labels sorted alphabetically.
Descriptions were taken from spaCy.explain().
Non-speech vocalizations (\texttt{NONSPEECH}) were manually identified.
Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PROPN & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the word) to its
``head''.

@@

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability. ~170 words => das wird beim folgenden Schreiben
% definitiv nichts werden
% intro
In order to assess data quality, we investigated if contrasting speech-related
events to events without speech lead to increased activation in areas known to
be involved in semantic processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns) contrasted to a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.
% data source
% data aligned by applying an affine transformation only are available in
% bold_dico_dico7Tad2grpbold7Tad.nii.gz.
% data aligned by non-linear warping are available in
% bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
We used a dataset providing blood oxygenation level-dependent (BOLD) functional
magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
\unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view) \citep{hanke2014audiomovie}.

@@

can be seen in Figure \ref{fig:reg-corr}}.

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to \texttt{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar
function from a word's onset to offset.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and events were as
boxcar function from a phoneme's onset to offset.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.

% low-level nuisance regressors
Lastly, we used continuous bins of information about auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) via Python script to
capture variance correlating with low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design motion parameter are
% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
% the processing applied to the input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time series.

% t-contrasts
The following three $t$-contrasts were defined:
1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

@@

% 2nd lvl
The second-level analysis which averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier deweighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
Figure \ref{fig:results} depicts the results of the three contrasts (z-threshold
Z>3.4; p<.05 cluster-corrected).
% COPE 1:
The contrast words > no-speech yielded four significant clusters (see Table
\ref{tab:cope1}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus and inferior
posterior supramarginal gyrus across the superior and middle temporal gyrus,
including parts of Heschl's gyrus and planum temporale.
% cluster 2
A second left cluster in (inferior) frontal regions, including precentral gyrus,
pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
% cluster 3
Similarly in the right hemisphere, one cluster spanning from the angular gyrus
across the superior and middle temporal gyrus but including frontal inferior
regions (pars opercularis and pars triangularis).
% cluster 4
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded nine significant
clusters (see Table \ref{tab:cope3}):
% cluster 1
one left lateralized cluster spanning from the angular gyrus across planum
temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
into the anterior middle temporal gyrus.
% cluster 2
A largely congruent but smaller cluster in the right hemisphere.
% cluster 3 & 5, and 4 & 6
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
% remaining 3 clusters of COPE 3
Three small clusters in the right occipital pole, right Heschl's gyrus and left
superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded four significant clusters (see Table \ref{tab:cope5}):
% cluster 1 & 2
two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
% variation in cluster 1 & 2 in comparison to COPE 1
In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
% cluster 3 & 4
Finally, two small right lateralized clusters in the right posterior cingulate
gyrus and right precuneus.

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/slicescolorbars}
    \caption{Results of the mixed-effects group-level (N=14) GLM $t$-contrasts
        for the audio-description of the movie ``Forrest Gump''.
        Significant clusters (Z>3.4, p<0.05 cluster-corrected) are overlaid on
        the MNI152 T1-weighted head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).}
    \label{fig:results}
\end{figure*} \todo{manual finalization of the figures spatial layout }

@@

% Discussion words > no-speech
For the contrast words > no-speech, results show increased hemodynamic activity
in a bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
These clusters resemble results of previous studies that implemented an ISC
approach to analyze fMRI data of naturalistic auditory stimuli
\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
% differences
We don't find significantly increased activations in midline areas (like the
posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
frontal cortex) which showed synchronized activity across subjects in previous
studies.
% Wilson (2008): ISC + GLM
In this regard, our results are similar to \citep{wilson2008beyond} who
implemented both an ISC and a GLM analysis. The findings by
\citep{wilson2008beyond} were that an ISC analysis yielded synchronized activity
in midline areas. But the GLM analysis contrasting blocks of listening to
narratives to blocks of a resting condition yielded decreased activity in
midline areas.
\todo{fun fact regarding reverse contrast (no-speech > words):
    clusters in posterior \& anterior cingulate (and subcallosal c. \& insulae
bilaterally); could be mentioned, must be mentioned? How shortly? No figure,
pls!}

% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation partially located in early sensory
regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently
adjacent regions bilaterally (planum temporale; superior temporal gyrus;
\citep{arsenault2015distributed, mesgarani2014phonetic}).
% why these contrasts nous & proper nouns
We chose nouns and proper nouns for these two contrasts because they represent
linguistically similar concepts but are uncorrelated in the German language and
stimulus (cf. Figure \ref{fig:reg-corr})
% coordinate conjunctions
We contrasted nouns and proper nouns respectively to coordinate conjunctions
because (proper) nouns and coordinate conjunctions are both linguistically
different and uncorrelated to coordinate conjunctions.
% “interpretation”
\todo{well what's combing up next is adventurous} Despite the fact that nouns
and proper nouns are uncorrelated, contrasts lead to spatially similar clusters
``which were not driven by a negative correlation of coordinate conjunctions
with the modeled time series (s. totally private data)''.
% why it's cool
Results suggest that our current annotation of naturalistic stimuli is of
``sufficient quality'' and can be used to create model-based analyses to test
neuroscientific hypotheses.

\todo[inline]{following stuff is still here but can probably be deleted}
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance

\section*{Data availability}
% aus der Schnitt-Annotation übernommen
\texttt{This section will be auto-generated.}

>>>>

\subsection*{Data Legend}
% TextGrid vs. TSV
The annotation is available in two different versions, both providing the same
information: a) as a text-based Praat TextGrid file, and b) as a text-based,
tab-separated value (TSV) formatted table.
% preview of following subsubsections
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text}, \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
\texttt{stop}, \texttt{vector}.

@@

\begin{table*}[t]
\caption{Simple part-of-speech tagging (\texttt{pos}) performed by the Python package spaCy \citep{spacy2}.
All 15 labels sorted alphabetically.
Descriptions were taken from spaCy.explain().
Non-speech vocalizations (\texttt{NONSPEECH}) were manually identified.
Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV
& \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PROPN & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
syntactic dependencies with other words within the same sentence.
% annotation scheme
Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
and is given in the format: ``arc label;word's head;word's child1, word's
child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
type of syntactic relation that connects a "child" (the current word) to its
``head''.

@@

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability. ~170 words => das wird beim folgenden Schreiben
% definitiv nichts werden intro
In order to assess the annotation's quality, we investigated if contrasting
speech-related events to events without speech lead to increased activation in
areas known to be involved in language processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns) contrasted to a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.
% data source data aligned by applying an affine transformation only are
% available in bold_dico_dico7Tad2grpbold7Tad.nii.gz.  data aligned by
% non-linear warping are available in bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
We used a dataset providing blood oxygenation level-dependent (BOLD) functional
magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
\unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view) \citep{hanke2014audiomovie}.

@@

can be seen in Figure \ref{fig:reg-corr}.}

@@

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors (see Table \ref{tab:regressors}) based on events drawn
from the annotation.
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to \texttt{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar function from a
word's onset to offset.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and modeled as
boxcar function from a phoneme's onset to offset.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
intervals without audible speech that lasted at least \unit[3.6]{s}.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous bins of information about auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) via Python script to
capture variance correlating with low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design motion parameter are
% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
% the processing applied to the input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time series.
% t-contrasts
The following three $t$-contrasts were defined:
1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

@@

% 2nd lvl
The second-level analysis that averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier deweighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

% Results
Figure \ref{fig:results} depicts the results of the three contrasts (z-threshold
Z>3.4; p<.05 cluster-corrected).
% COPE 1:
The contrast words > no-speech yielded four significant clusters (see Table
\ref{tab:cope1}):
% cluster 1
one left-lateralized cluster spanning from the angular gyrus and inferior
posterior supramarginal gyrus across the superior and middle temporal gyrus,
including parts of Heschl's gyrus and planum temporale.
% cluster 2
A second left cluster in (inferior) frontal regions, including precentral gyrus,
pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
% cluster 3
Similarly in the right hemisphere, one cluster spanning from the angular gyrus
across the superior and middle temporal gyrus but including frontal inferior
regions (pars opercularis and pars triangularis).
% cluster 4
A fourth significant cluster is located in the left thalamus.

% COPE 3
The contrast proper nouns > coordinate conjunctions yielded nine significant
clusters (see Table \ref{tab:cope3}):
% cluster 1
one left-lateralized cluster spanning from the angular gyrus across planum
temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
into the anterior middle temporal gyrus.
% cluster 2
A largely congruent but smaller cluster in the right hemisphere.
% cluster 3 & 5, and 4 & 6
Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
% remaining 3 clusters of COPE 3
Three small clusters in the right occipital pole, right Heschl's gyrus and left
superior lateral occipital pole.

% COPE 5
The contrast nouns > coordinate conjunctions yielded four significant clusters
(see Table \ref{tab:cope5}):
% cluster 1 & 2
two clusters that are slightly smaller than lateral temporal clusters of
contrast nouns > coordinate conjunction.
% variation in cluster 1 & 2 in comparison to COPE 1
In this case, spanning from angular gyrus in the left hemisphere and from planum
temporale in the right hemisphere into the anterior part of superior temporal
cortex.
% cluster 3 & 4
Finally, two small right-lateralized clusters in the right posterior cingulate
gyrus and right precuneus.

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/slicescolorbars}
    \caption{Results of the mixed-effects group-level (N=14) GLM $t$-contrasts
        for the audio-description of the movie ``Forrest Gump''.
        Significant clusters (Z>3.4, p<0.05 cluster-corrected) are overlaid on
        the MNI152 T1-weighted head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).}
    \label{fig:results}
\end{figure*}

@@

% Discussion words > no-speech
For the contrast words > no-speech, results show increased hemodynamic activity
in a bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
These clusters resemble results of previous studies that implemented an ISC
approach to analyze fMRI data of naturalistic auditory stimuli
\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
% differences
We don't find significantly increased activations in midline areas (like the
posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
frontal cortex) which showed synchronized activity across subjects in previous
studies.
% Wilson (2008): ISC + GLM
In this regard, our results are similar to \citep{wilson2008beyond} who
implemented both an ISC and a GLM analysis. In this study, the ISC analysis
showed synchronized activity in midline areas but the GLM analysis contrasting
blocks of listening to narratives to blocks of a resting condition showed
significantly decreased activity in these areas.
\todo[inline]{our reverse contrast (no-speech > words): clusters in posterior \&
anterior cingulate (and subcallosal c. \& insulae bilaterally); I think opening
the pandora's box of the reverse contrasts is not worth it here}

% (proper) nouns > con
The two contrasts that contrasted nouns and proper nouns respectively to
coordinate junctions yielded increased activation partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% why these contrasts nous & proper nouns
We chose nouns and proper nouns for these two contrasts because they represent
linguistically similar concepts but are uncorrelated in the German language and
stimulus (cf. Figure \ref{fig:reg-corr})
% coordinate conjunctions
We contrasted nouns and proper nouns respectively to coordinate conjunctions
because (proper) nouns are linguistically different to coordinate conjunctions
as well as uncorrelated.
% “interpretation”
\todo[inline]{well what's coming up next is adventurous} Both contrasts lead to
largely spatially congruent clusters despite the fact that nouns and proper
nouns are uncorrelated.
% not driven by coordinate conjunction regressors
We confirmed the validity of these interpretation by testing if the spatial
congruency could be attributed to a negative correlation of coordinate
conjunctions with the modeled time series which turned out to be not the case.
% why it's cool
In summary, the results of our exploratory analyses suggests that the
annotation of speech meets the quality requirements to be used as the basis for
model-based analyses that investigate language perception under more
ecologically valid conditions.\todo{might be a little humble}

\section*{Data availability}
\todo{cf. other F1000 papers but probably a gift for the master}
\texttt{This section will be auto-generated.}
